Sweep A - general experiment analysis.

### 2018-03-10 voltagebudget/analysis/sweep_A_analysis.Rmd
Update sweep_A vis

```{r, message=FALSE}
exp <- "58"
freqs <- c("4", "8", "12", "20", "24", "30")

results <- NULL
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-0.2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df %>%
    filter(n_spikes > 0) -> df

@@

results$freq <- factor(results$freq, levels=freqs)
rm(df, exp, freq, freqs, levels, name)
```

@@

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As, y=n_spikes, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As, y=variances, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

- why is var so variable?

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=As, y=errors, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=variances, y=errors, color=freq)) +
  geom_point(size=.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=3.5}
results %>% 
  ggplot(aes(x=variances, y=errors, color=freq)) +
  geom_point(size=.05) + 
  facet_grid(freq~.) +
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

@@

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=n_spikes, y=variances, color=freq)) +
  geom_point(size=0.1) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=n_spikes, y=errors, color=freq)) +
  geom_point(size=0.1) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

@@

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As, y=V_osc, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=2, fig.height=1.5}
results %>% 
  ggplot(aes(x=V_osc, y=V_comp, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.25, fig.height=3.5}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=V_comp/V_b, color=As)) +
  geom_line() + 
  theme_classic() +
  facet_grid(freq~.) +
  # scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=n_spikes, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=variances, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_osc/V_b, y=errors, color=freq)) +
  geom_line() + 
  theme_classic() +
  xlim(0, 1.5) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_comp/V_b, y=errors, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  xlim(0, 0.7) +
  ylim(0, 0.010) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(V_comp <= V_osc - min(V_osc)) %>% 
  ggplot(aes(x=V_comp/V_b, y=errors, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  xlim(0, 0.7) +
  ylim(0, 0.010) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_comp/V_osc, y=variances, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  # xlim(0, 0.7) +
  # ylim(0, 0.010) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_comp/V_osc, y=errors, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  # xlim(0, 0.7) +
  # ylim(0, 0.010) +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  ggplot(aes(x=V_comp/V_b, y=variances, color=freq)) +
  geom_point(size=0.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

>>>>

```{r, message=FALSE}
exp <- "71"
freqs <- c("8", "12", "20", "24", "30")

results <- NULL
for(freq in freqs){
  name <- paste("../data/exp", exp, "_d-2e-3_f", freq, ".csv", sep="")
  df <- read_csv(paste(name, sep=""))
  df %>%
    filter(n_spikes > 0) -> df

@@

results$freq <- factor(results$freq, levels=freqs)
rm(df, exp, freq, freqs, name)
```

@@

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As, y=n_spikes_pop, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As, y=variances_pop, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=As, y=errors_pop, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=variances_pop, y=errors_pop, color=freq)) +
  geom_point(size=.05) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=3.5}
results %>% 
  ggplot(aes(x=variances_pop, y=errors_pop, color=freq)) +
  geom_point(size=.05) + 
  facet_grid(freq~.) +
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

@@

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=n_spikes_pop, y=variances_pop, color=freq)) +
  geom_point(size=0.1) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.6, fig.height=1.6}
results %>% 
  filter(rank == 0) %>% 
  ggplot(aes(x=n_spikes_pop, y=errors_pop, color=freq)) +
  geom_point(size=0.1) + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

@@

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As*1e9, y=V_osc, color=freq)) +
  geom_point() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

- TODO: port over Vo/Vc plots....
